MSAD_PCA_Walkthrough

### 2017-01-24 Simulation_Vignette.Rmd
Alarm identification and removal fixed. now the code is finding one alarm-worthy observation out of 1440 observations after training on 2880 observations. My instinct is that the T2 statistic is throwing the alarm, as there are 2.5x as many observations flagged by the T2 statistic as by the SPE statistic.

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).
